Exploratory Data Analysis

### 2023-10-18 analysis/eda.qmd
changes
Added setup.R script
table 1 and 2

```{r setup, warning=FALSE, message=FALSE}

library(tidyverse)
library(dagitty)
library(ggdag)
library(MetBrewer)
library(here)
library(broom) # For converting model output to data frames

# set theme of all DAGs to `theme_dag()`
theme_set(theme_dag(base_family = "Noah"))

@@

```{r aggressiveness, warning=FALSE, message=FALSE}
#| fig-width: 10

>>>>

{{< include 00-setup.qmd >}}

```{r table1, warning=FALSE, message=FALSE}
#| fig-width: 10

table_one_vars <- c("age", "sex", "race", "ethnicity", "time_symptoms_to_ed", "sbp_baseline", "nihss_baseline", "gcs_baseline", "ich_laterality", "htn", "dm2", "stroke", "tobacco", "ich_location", "ich_volume_baseline", "ivh_volume_baseline", "study")

table1 <- data |>
  select(table_one_vars) |>
  tbl_summary(by = ich_laterality) |>
  add_p() |>
  add_overall() |>
  bold_labels()

table1

## Aggressiveness of Care

First, we will explore if patients with **left hemispheric** injuries receive less aggressive care.

### Neurosurgical Intervention

```{r neurosurgery, warning=FALSE, message=FALSE}

table_two_vars <- c("neurosurgery_evac", "evd", "tracheostomy", "peg", "ich_laterality", "comfort_care_binary", "")

table2 <- data |>
  select(table_two_vars) |>
  tbl_summary(by = ich_laterality) |>
  add_p() |>
  add_overall() |>
  bold_labels()

table2

@@

```{r eda, warning=FALSE, message=FALSE}
#| fig-width: 10
